Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-03-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
latex clean up

\begin{figure}[p]
	\centering
	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_5mm_10s_color}
	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_10mm_10s_color}\\
	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_20mm_10s_color}
	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_40mm_10s_color}
	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_80mm_10s_color}\\
	 \caption[Comparison images of intensity fields derived from the video images of the natural gas fueled fire]{Comparison images of intensity fields derived from the video images of the natural gas fueled fire using Streams. The images, starting with the upper left, were generated with 5 mm, 10 mm, 20 mm, 40 mm and 80 mm resolutions.}
	 \label{Intensity}
\end{figure}

@@

A free standing steel frame wall with a 12.7~mm thick, 2.44~m high by 1.22~m wide, calcium silicate board face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux. Marinite Type I is the commercial name of the non-combustible board used in these experiments.  It is normally used as a fire-resistant thermal insulation that also has structural strength. 90~\% of the board is composed of calcium silicate and calcium meta-silicate.  The remaining 10~\% of the board is composed of a combination of organic fibers, fiber glass filament and crystalline silica (quartz) ref BNZ MSDS.  Material properties that impact heat transfer were selected from the manufacturer's literature and are presented in the table below ref BNZ Marinite I.   
\begin{table}
	\centering
\begin{tabular}{|c|c|c|c|c|}
	\hline Density (kg/m$^3&)  &Thermal Conductivity   & Specific Heat  &  &  \\ 
	\hline   & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
	\hline 737  & 24 & 0.13 & 93 & 0.28 \\ 
	\hline  & 205 & 0.12  & 205 & 0.30 \\ 
	\hline  & 316 & 0.11 & 316 & 0.32 \\ 
	\hline  & 425 & 0.12 & 425 & 0.34 \\ 
	\hline  & 538 & 0.12 &  &  \\ 
	\hline 
\end{tabular} 
\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ Marinite I.}
\label{tab:Marinite_Thermal_Properties}
\end{table}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_61m_RepsAvg}
	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_31m_RepsAvg}\\
	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_15m_RepsAvg}
	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0m_RepsAvg}\\
	\caption[Wall heat fluxes along the centerline of the gasoline fueled burner]{Wall heat fluxes along the centerline of the gasoline fueled burner.  The heat fluxes are averages of three replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top left position and moving from left to right the distances are 0.61~m, 0.31~m,0.15~m,and 0~m.}
	\label{IW_HFC_TWGAS}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/nctw_ng_heatflux}\\
	\caption[Summary of wall heat fluxes along the centerline of the natural gas fueled burner]{Summary of the heat flux to the non-combustible wall along the verticle centerline of the natural gas fueled burner compared to the position away from the wall.}
	\label{nctw_ng_heatflux}
\end{figure}

@@

According to the United States Geological Survey, most gypsum in the United States is used to make wallboards for homes and other structures.  A typical home in the United States contains more than 7 metric tons of gypsum ref USGS website http://minerals.usgs.gov/minerals/pubs/commodity/gypsum/.  As defined by ASTM, gypsum wallboard is gypsum board designed for use on walls, ceilings, or partitions and that affords a surface suitable to recieve decoration  ref ATSM 1396. The ASTM standard further describes gypsum wallboard as having a noncombustible core, surfaced with paper bonded to the core. By weight, wallboard is composed of more than 85~\% gypsum, less than 10~\% cellulose, less than 3~\% starch and approximately 1~\% of both crystalline silica and fibrous glass.  Chemically gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$  2H$_{2}O) .  By weight pure gypsum is approximately 79~\% calcium sulfate and 21~\% chemically bound water ref Lawson 1977.

@@

 \begin{figure}[p]
 	\centering
 	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
 	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Surface_Offset_Avg}\\
 	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Plume_Avg_Avg}\\
 	\caption[Averaged peak wall and plume temperatures for the natural gas burner]{Averaged peak wall and plume temperatures for the natural gas burner fires at several different positions from the instrumented gypsum board wall.  The positions ranged from 0.3 m away from the wall to physically touching the wall, 0.0 m.}
 	\label{IWGB_NG_Temp_FrontSet}
 \end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
	\caption[Averaged peak heat flux on the gypsum board wall for the natural gas burner fires.]{Averaged peak heat flux on the gypsum board wall along the vertical centerline and edge of the natural gas burner fires. }
	\label{IWGB_NG_Temp_RearCenter}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
	\includegraphics[width=4.5in]{../Figures/IWGB_GAS_TC_Surface_Center_Avg}\\
	\includegraphics[width=4.5in]{../Figures/IWGB_PUF_TC_Surface_Center_Avg}\\
	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires. The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
	\label{IWGB_Temp_Comp_FrontCenter}
\end{figure}

>>>>

\begin{figure}[p]
	\centering
	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80_1_GS_5mm_10s_color}
	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80_1_GS_10mm_10s_color}\\
	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80_1_GS_20mm_10s_color}
	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80_1_GS_40mm_10s_color}
	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80_1_GS_80mm_10s_color}\\
	 \caption[Comparison images of intensity fields derived from the video images of the natural gas fueled fire]{Comparison images of intensity fields derived from the video images of the natural gas fueled fire using Streams. The images, starting with the upper left, were generated with 5~mm, 10~mm, 20~mm, 40~mm and 80~mm resolutions.}
	 \label{Intensity}
\end{figure}

@@

A free standing steel frame wall with a 12.7~mm thick, 2.44~m high by 1.22~m wide, calcium silicate board face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux. Marinite Type I is the commercial name of the non-combustible board used in these experiments.  It is normally used as a fire-resistant thermal insulation that also has structural strength. 90~\% of the board is composed of calcium silicate and calcium meta-silicate.  The remaining 10~\% of the board is composed of a combination of organic fibers, fiber glass filament and crystalline silica (quartz) ref BNZ MSDS.  Material properties that impact heat transfer were selected from the manufacturer's literature and are presented in the table below ref BNZ Marinite I.   
\begin{table}
	\centering
\begin{tabular}{|c|c|c|c|c|}
	\hline Density & \multicolumn{2}{c|}{Thermal Conductivity} & \multicolumn{2}{c|}{Specific Heat}   \\ 
    \hline (kg/m$^3$) & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
	\hline 737  & 24 & 0.13 & 93 & 0.28 \\ 
	\hline  & 205 & 0.12  & 205 & 0.30 \\ 
	\hline  & 316 & 0.11 & 316 & 0.32 \\ 
	\hline  & 425 & 0.12 & 425 & 0.34 \\ 
	\hline  & 538 & 0.12 &  &  \\ 
	\hline 
\end{tabular} 
\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ Marinite I.}
\label{tab:Marinite_Thermal_Properties}
\end{table}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_61m_Reps_Avg}
	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_31m_Reps_Avg}\\
	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_15m_Reps_Avg}
	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0m_Reps_Avg}\\
	\caption[Wall heat fluxes along the centerline of the gasoline fueled burner]{Wall heat fluxes along the centerline of the gasoline fueled burner.  The heat fluxes are averages of three replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top left position and moving from left to right the distances are 0.61~m, 0.31~m,0.15~m,and 0~m.}
	\label{IW_HFC_TWGAS}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/NCTW_NG_HF_Center_Avg}\\
	\caption[Summary of wall heat fluxes along the centerline of the natural gas fueled burner]{Summary of the heat flux to the non-combustible wall along the verticle centerline of the natural gas fueled burner compared to the position away from the wall.}
	\label{nctw_ng_heatflux}
\end{figure}

@@

According to the United States Geological Survey, most gypsum in the United States is used to make wallboards for homes and other structures.  A typical home in the United States contains more than 7 metric tons of gypsum ref USGS website http://minerals.usgs.gov/minerals/pubs/commodity/gypsum/.  As defined by ASTM, gypsum wallboard is gypsum board designed for use on walls, ceilings, or partitions and that affords a surface suitable to recieve decoration  ref ATSM 1396. The ASTM standard further describes gypsum wallboard as having a noncombustible core, surfaced with paper bonded to the core. By weight, wallboard is composed of more than 85~\% gypsum, less than 10~\% cellulose, less than 3~\% starch and approximately 1~\% of both crystalline silica and fibrous glass.  Chemically gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$2H$_{2}$O) .  By weight pure gypsum is approximately 79~\% calcium sulfate and 21~\% chemically bound water ref Lawson 1977.

@@

 \begin{figure}[p]
 	\centering
 	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
 	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Surface_Offset_Avg}\\
 	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Plume_Avg}\\
 	\caption[Averaged peak wall and plume temperatures for the natural gas burner]{Averaged peak wall and plume temperatures for the natural gas burner fires at several different positions from the instrumented gypsum board wall.  The positions ranged from 0.3 m away from the wall to physically touching the wall, 0.0 m.}
 	\label{IWGB_NG_Temp_FrontSet}
 \end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
	\caption[Averaged peak heat flux on the gypsum board wall for the natural gas burner fires.]{Averaged peak heat flux on the gypsum board wall along the vertical centerline and edge of the natural gas burner fires. }
	\label{IWGB_NG_HF_RearCenter}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
	\includegraphics[width=4.in]{../Figures/IWGB_GAS_TC_Surface_Center_Avg}\\
	\includegraphics[width=4.in]{../Figures/IWGB_PUF_TC_Surface_Center_Avg}\\
	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires. The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
	\label{IWGB_Temp_Comp_FrontCenter}
\end{figure}
